Watch Out for the Bully! Job Interference Study on Dragonfly Network

### 2016-04-09 intro.tex
add SlimFly citation
intro trivia

Recent studies suggest that random job placement coupled with adaptive routing can alleviate local congestion, eliminate hot-spots and reach load-balance for dragonfly networks~\cite{jain-sc14, bhatele-sc11, brandt2014}. 
These works explore the possible job placement and routing configurations that could optimize the overall network performance without examining how different configurations impact the progress of individual applications.
In this paper, we study the implications of contention for shared network links in the context of multiple HPC applications running on dragonfly systems when different job placement and routing configurations are in use.
Our analyses focus on the overall network performance as well as the performance of concurrently executing applications in the presence of network contention.

@@

We choose three representative HPC applications from the DOE Design Forward Project~\cite{designforward-webpage} to analyze the interference among them. Our study is based on simulation with CODES, a high-fidelity, flit-level HPC network simulation toolkit~\cite{codes}.
For each application, we examine its performance with two job placement policies and three routing policies.
We make the following observations through extensive simulations.

>>>>

Recent studies suggest that random node allocation for parallel jobs, coupled
with adaptive routing, can alleviate local congestion, eliminate hot-spots and achieve load-balancing for dragonfly networks~\cite{jain-sc14, bhatele-sc11, brandt2014}. 
These works explore the possible job placement and routing configurations that could optimize the overall network performance without examining how different configurations impact the progress of individual applications.
In this paper, we study the implications of contention for shared network links in the context of multiple HPC applications running on dragonfly systems when different job placement and routing configurations are in use.
Our analyses focus on the overall network performance as well as the performance of concurrently executing applications in the presence of network contention.

@@

We choose three representative HPC applications from the DOE Design Forward Project~\cite{designforward-webpage} and analyze the interference among them. Our study is based on simulation with CODES, a high-fidelity, flit-level HPC network simulation toolkit~\cite{misbah-tpds}. 
For each application, we examine its performance with two job placement policies and three routing policies.
We make the following observations through extensive simulations.
